Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-01 WSSSPE1_report/WSSSPE1_summary_report.tex
some text changes

In conclusion, there are clear distinctions in the characteristics and the
kinds of challenges faced between generic utility oriented and specific
scientific domain oriented software projects. In terms of career paths of
original developers, it appears that the career paths for utility software
developers are broader compared to the developers of scientific software.
However, it appears that in the case of scientific software, core competencies
of original developers tend to be domain science who happen to be the coders of
their software. As projects as a whole, the small-scale, specific software have
a lower risk and cost in terms of sustaining as compared to utility software.
Often the sustainability of such projects is achieved by the fact that the core
developer or team heavily utilizes the software for their science, eg.
\emph{R/qtl, PETSc}. Furthermore, the development of scientific software
requires more scientific skills compared with those of utility software. This
diminishes the need of specialist programmers and practices in many cases where
the bulk of development is carried out by a domain scientist. With these
inferences, we believe that separate guidelines and/or principles for
sustainability be defined for each category of software projects in science and
they be given separate treatment.

>>>>

In conclusion, we find that there are distinctions in the characteristics and
the kinds of challenges faced between generic utility and specific scientific
domain software projects. In terms of career paths of original developers, it
appears that the career paths for utility software developers are broader
compared to the developers of scientific software.  However, it appears that in
the case of scientific software, core competencies of original developers tend
to be domain science who happen to be the coders of their software. As projects
as a whole, the small-scale, specific software have a lower risk and cost in
terms of sustaining as compared to utility software.  Often the sustainability
of such projects is achieved by the fact that the core developer or team
heavily utilizes the software for their science, eg.  \emph{R/qtl, PETSc}.
Furthermore, the development of scientific software requires more scientific
skills compared with those of utility software. This diminishes the need of
specialist programmers and practices in many cases where the bulk of
development is carried out by a domain scientist. With these inferences, we
believe that separate guidelines and/or principles for sustainability be
defined and practiced for each category of scientific software and they be
given separate treatment.
